### 2018-05-31 algorithm.tex
dual loop: holding expenditure shares fixed within inner loop. even for large gamma, converges slowly

Taking the market clearing condition,
\begin{equation}
	R_{njt} = \sum_{m=1}^N
		d_{mnjt}
		\left[
			\alpha_{jt}
			\left(
				\sum_{k=1}^J\beta_k R_{mkt} - S_{mt}
			\right)
			+ \sum_{k=1}^J\gamma_{jk}R_{mkt}
		\right],
\end{equation}
\[
	R_{njt}\varrho_{njt}^{\theta} = \sum_{m=1}^N
		(\kappa_{mnjt} P_{mjt})^{\theta}
		\left[
			\alpha_{jt}
			\left(
				\sum_{k=1}^J\beta_k R_{mkt} - S_{mt}
			\right)
			+ \sum_{k=1}^J\gamma_{jk}R_{mkt}
		\right],
\]
\begin{equation}\label{eq:market_clearing}
	\varrho_{njt} = R_{njt}^{-1/\theta}
	\left\{
	\sum_{m=1}^N
		(\kappa_{mnjt} P_{mjt})^{\theta}
		\left[
			\alpha_{jt}
			\left(
				\sum_{k=1}^J\beta_k R_{mkt} - S_{mt}
			\right)
			+ \sum_{k=1}^J\gamma_{jk}R_{mkt}
		\right]
	\right\}^{1/\theta}.
\end{equation}
Here both $R_{njt}$ and $\varrho_{njt}$ depend on equilibrium prices. But starting from a guess for $R$ (say, the autarky equilibrium), we can easily compute a shadow price $\varrho$ supporting that allocation. 
\begin{enumerate}
	\item Set $R_{njt}^{(0)}$ and $P_{njt}^{(0)}$ to the autarky equilibrium value or other suitable starting value.
	\item Given $R_{njt}^{(k)}$ and $P_{njt}^{(k)}$, solve for $\varrho_{njt}^{(k+1)}$ using equation \eqref{eq:market_clearing}.
	\item Solve for $w_{njt}^{(k+1)}$ and $P_{njt}^{(k+1)}$ using \eqref{eq:wage} and \eqref{eq:price}.
	\item Calculate $R_{njt}^{(k+1)} = w_{njt}^{(k+1)}L_{njt}/\beta_j$.
	\item Go back to Step 2 and repeat until convergence.
\end{enumerate}
Typically, this converges in 4--6 steps. This might even be a contraction mapping.

@@

>>>>

Taking the market clearing condition,
\begin{equation}
	R_{njt} = \sum_{m=1}^N
		d_{mnjt}
		\left[
			\alpha_{jt}
			\left(
				\sum_{k=1}^J\beta_k R_{mkt} - S_{mt}
			\right)
			+ \sum_{k=1}^J\gamma_{jk}R_{mkt}
		\right],
\end{equation}
\[
	R_{njt}\varrho_{njt}^{\theta} = \sum_{m=1}^N
		(\kappa_{mnjt} P_{mjt})^{\theta}
		\left[
			\alpha_{jt}
			\left(
				\sum_{k=1}^J\beta_k R_{mkt} - S_{mt}
			\right)
			+ \sum_{k=1}^J\gamma_{jk}R_{mkt}
		\right],
\]
\begin{equation}\label{eq:market_clearing}
	\varrho_{njt} = R_{njt}^{-1/\theta}
	\left\{
	\sum_{m=1}^N
		(\kappa_{mnjt} P_{mjt})^{\theta}
		\left[
			\alpha_{jt}
			\left(
				\sum_{k=1}^J\beta_k R_{mkt} - S_{mt}
			\right)
			+ \sum_{k=1}^J\gamma_{jk}R_{mkt}
		\right]
	\right\}^{1/\theta}.
\end{equation}
Here both $R_{njt}$ and $\varrho_{njt}$ depend on equilibrium prices. But starting from a guess for $R$ (say, the autarky equilibrium), we can easily compute a shadow price $\varrho$ supporting that allocation. 
\begin{enumerate}
	\item Set $R_{njt}^{(0)}$ and $P_{njt}^{(0)}$ to the autarky equilibrium value or other suitable starting value.
	\item Given $R_{njt}^{(k)}$ and $P_{njt}^{(k)}$, solve for $\varrho_{njt}^{(k+1)}$ using equation \eqref{eq:market_clearing}.
	\item Solve for $w_{njt}^{(k+1)}$ and $P_{njt}^{(k+1)}$ using \eqref{eq:wage} and \eqref{eq:price}.
	\item Calculate $R_{njt}^{(k+1)} = w_{njt}^{(k+1)}L_{njt}/\beta_j$. (This step sounds the most divergent, nothing ensures that relative sectoral revenue shares will remain close to equilibrium.)
	\item Go back to Step 2 and repeat until convergence.
\end{enumerate}
Typically, this converges in 4--6 steps. This might even be a contraction mapping.

@@

\subsection{Dual loop}
What are the sectoral expenditures across countries?
\[
E_{mjt} = 			\alpha_{jt}
			\left(
				\sum_{k=1}^J\beta_k R_{mkt} - S_{mt}
			\right)
			+ \sum_{k=1}^J\gamma_{jk}R_{mkt}
\]
The sectoral expenditure share is
\begin{equation}\label{eq:sectoral_share}
e_{mjt} = \frac
	{\sum_{k=1}^J(\alpha_{jt}\beta_k+\gamma_{jk}) R_{mkt} - S_{mt}}
	{\sum_{k=1}^J R_{mkt}-S_{mt}}.
\end{equation}
Even if $S_{mt}=0$, this is not constant, because it depends on the revenue distribution across sectors. If a country has a comparative advantage in car production, it will have high revenue (not expenditure) in cars. But then it will have high expenditure in car inputs.

For the purposes of finding the equilibrium, fix sectoral expenditure shares in each country. (We can start from free-trade expenditure shares, which are exogenous and are the same across countries.) Rewriting the equilibrium condition,
\[
	\varrho_{njt} = R_{njt}^{-1/\theta}
	\left[
	\sum_{m=1}^N
		(\kappa_{mnjt} P_{mjt})^{\theta}
		e_{mjt}
		\left(
			\sum_{k=1}^J R_{mkt}
			-S_{mt}
		\right)
	\right]^{1/\theta}.
\]
Inner loop: solve for $\varrho$ and $R$, holding $e$ fixed. This does not allow for divergence across sectors off the equilibrium path, as the sectoral composition is held fixed.

Middle loop: given the solved $R$s, calculate the new expenditure shares from equation \eqref{eq:sectoral_share}. This may be dampened.
